%!TEX root=main.tex
%
% Syllabus and Schedule
%

\begin{enumerate}
	\item Introduction (15 mins)
	\begin{enumerate}
	\itemsep-0.4em	
		\item Rendering
		\item Problems in rendering
		\begin{enumerate}%[label=$\star$]
		\itemsep-0.6em	
			\item integration
			\item reconstruction
			\item iterplay
		\end{enumerate}	
		\item The role of sampling.
		\item Practice
		\begin{enumerate}
		\itemsep-0.6em
			\item How samples are used in a typical renderer. 
			\item Show black box data structure with samples
			\item Show how renderer uses these
			\item Explain how dimensionality is handled…
		\end{enumerate}
		\item Error: Sources and and how they manifest
	\end{enumerate}
	\item State of the art in sampling (10 mins) 
	\begin{enumerate}
	\itemsep-0.4em	
		\item Classical: Random, Jittered, Latin HC …
		\item QMC: Sobol, Hammersley 
		\item Blue Noise: Poisson disk, CCVT, Victor’s 
		\item Spectral specification
	\end{enumerate}
	\item The reconstruction problem (10 mins)
	\begin{enumerate}
	\itemsep-0.4em
		\item Define problem
		\item Signal processing: Nyquist, Balakrishnan, Dippe and Wold, …
		\item Vision, perception: Yellott, Ulichney ...
		\item Graphics: Mitchell, cook, shirley, …
		\item transition via Mitchell’s analysis
		\item Quality assessment? \\
		(Alvy Ray Smith (1995) has emphatically pointed out, thinking of pixels as small squares with 
		finite area is an incorrect mental model that leads to a series of errors)  
	\end{enumerate}
	\textbf{Break (5 mins) : Questions?}
	\item Integration using stochastic sampling (30 mins) 
	\begin{enumerate}
	\itemsep-0.4em
		\item Define problem
		\item Error in the fourier domain
		\item Errors in integration due to sampling (30 mins)
		\begin{enumerate}
		\itemsep-0.6em
			\item The canonical domain
			\item From first principles
			\item MSE vs variance/bias. Relevance of phase.
			\item Measuring/predicting error
			\begin{enumerate}
			\itemsep-0.6em
				\item periodogram: show examples in case study
				\item amplitude of the expected Fourier spectrum: show examples 
				\item behaviour at low frequencies (slope of the spectrum as it approaches DC): show 
				all examples in case study
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}
	\textbf{Break (5 mins) : Questions?} 
	\item Extensions (15 mins)
	\begin{enumerate}
	\itemsep-0.4em
		\item Domain 
		\begin{enumerate} 
		\itemsep-0.6em
			\item P’boue, Gurprit et al’s
			\item Differential Domain Sampling
			\item Spherical Fibonacci lattice (QMC)
		\end{enumerate}
		\item Gradients
		\begin{enumerate}
			\item Jaakko and co’s two gradient domain papers
		\end{enumerate}
	\end{enumerate}
	\item Case study empirical comparisons (15 mins) 	
	\begin{enumerate}
	\itemsep-0.4em
		\item Mixture of Gaussians
		\item Mixture of Gaussians with step edges
		\item Canonical rendering examples
	\end{enumerate}
	\item Conclusion (5 mins)
\end{enumerate}






